\documentclass[10pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.0cm,right=1.06cm,bottom=1.0cm]{geometry}

\pagestyle{empty}
\begin{document}

% --- HEADER ---
\begin{center}
    \textbf{\Large Jorge Manuel Torre} \\
    \vspace{2pt}
    \hrulefill \\
    \vspace{2pt}
    Ashburn, VA \textbullet \ \href{mailto:jmt1006@vt.edu}{jmt1006@vt.edu} \textbullet \ 571-888-4832 \textbullet \ \href{https://www.linkedin.com/in/jmt1006/}{linkedin.com/in/jmt1006} \textbullet \ \href{https://github.com/jmtorr3}{github.com/jmtorr3}
\end{center}

\vspace{-5pt}

% --- EDUCATION ---
\begin{center}
    \textbf{\large Education}
\end{center}
\vspace{-5pt}

\textbf{Virginia Tech} \hfill Blacksburg, VA \\
B.S. Computer Science. \hfill May 2026

\textbf{Relevant Coursework:} Linux Kernel Programming, Software Reverse Engineering, Security of AI, Computer Architecture, Computer Systems, Data Structures \& Algorithms.

\vspace{5pt}

% --- PROJECTS & RESEARCH ---
\begin{center}
    \textbf{\large Technical Projects}
\end{center}
\vspace{-5pt}

\textbf{Garage64: Custom Entity Model Studio} \textbullet \ \href{https://github.com/jmtorr3/Garage64}{GitHub} \hfill Spring 2026 \\
\textit{React, Three.js, Django, SQLite, Docker}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
  \item Built a full-stack web application that serves as a complete suite for designing and exporting custom Minecraft car models (OptiFine CEM) and texture packs.
  \item Engineered a React and Three.js frontend to provide a real-time 3D workspace, allowing users to dynamically compose vehicles by swapping parts and applying custom paint textures.
  \item Developed a Django REST API to manage the entity data structure and created a one-click export button that generates ready to use .jem and .jpm asset files.
\end{itemize}

\vspace{3pt}


\textbf{ParkGrid: Campus Parking Solution} \textbullet \ \href{https://github.com/jmtorr3/smart-parking}{GitHub} \hfill Winter 2025 \\
\textit{React, Django, PostgreSQL, Docker, Python}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
  \item Served as the technical lead for a 5-person team, directing project milestones and taking primary ownership of the original core full-stack application
  \item Partnered with one developer to design the relational databse architecture and transition the initial prototype into a more polished version
  \item Developed a Python simulator to generate high frequency occupancy data ensuring the PostgreSQL database could handle simultaneous sensor updates accurately.
\end{itemize}

\vspace{3pt}

\textbf{Nintendo DS Security Analysis} \hfill Winter 2024 \\
\textit{Assembly, DeSmuME, Ghidra}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Executed dynamic binary analysis on the Nintendo DS architecture using a virtualized Debian/Windows lab environment provided by the advanced Software Reverse Engineering curriculum.
    \item Reverse-engineered the proprietary Gen 5 Linear Congruential Generator (LCG) encryption protocol to decrypt 220-byte save file structures.
    \item Developed a custom Python tool to calculate dynamic block shuffling permutations based on the PID bitmask, enabling the modification of binary data without checksum corruption.
\end{itemize}

\vspace{3pt}

\textbf{Experimental Proxmox Home Lab} \hfill 2021 -- Present \\
\textit{Proxmox, Debian, Ubuntu, NixOS, Docker}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
  \item Built a home lab environment on Proxmox to host, manage, and experiment with various things.
  \item Designed and troubleshot network topologies, actively experimenting with OPNsense firewall configurations and secure jumpbox deployments to manage remote access across virtualized environments.
  \item Configured reproducible development environments to serve as a dedicated workspace for Linux kernel programming, system-level testing, and occasionally self-hosting personal services.
\end{itemize}

\vspace{3pt}

% --- LEADERSHIP ---
\begin{center}
    \textbf{\large Leadership \& Community}
\end{center}
\vspace{-5pt}

\textbf{Garage32 (Community Project)} \textbullet \ \href{https://github.com/jmtorr3/Garage32}{GitHub} \hfill Project Lead \\
\vspace{-2pt}
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
  \item Managed development and distribution of a graphical asset pack, achieving \textbf{500+ downloads} and positive community sentiment.
\end{itemize}

\vspace{5pt}

% --- SKILLS ---
\begin{center}
    \textbf{\large Skills}
\end{center}
\vspace{-5pt}

\textbf{Languages:} C, C++, Python, Java, Assembly (ARM), SQL, JavaScript \\
\textbf{Systems \& Security:} Reverse Engineering, Ghidra, Linux Kernel, ACID Transactions, Concurrency, Cryptography (LCG) \\
\textbf{Infrastructure:} NixOS, Proxmox, Docker, PostgreSQL, LaTeX, Git, CI/CD

\end{document}
